%!TeX TXS-program:bibliography = txs:///biber
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{booktabs, float, color, colortbl, graphicx, ragged2e, setspace, threeparttablex, threeparttable, longtable, placeins, booktabs, float, tabularx}
\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{acronym}
\usepackage{csquotes}
\usepackage[plainpages=false]{hyperref}
\usepackage{todonotes}
\usepackage{fullpage}


\hypersetup{%
	%backref=true,%
    plainpages=false,%
	naturalnames=true,%
	bookmarksnumbered=true,%
	bookmarksopen=false,%
	colorlinks=true,%
	urlcolor=black,
	linkcolor=black,%
	filecolor=black,%
	citecolor=black,%
	%pagecolor=myblue,%
	%pdftitle={\mytitle},%
	pdfpagemode=UseOutlines%
	%pdfauthor={\myauthors},%
	%pdfsubject={\myshorttitle}
}
\usepackage[natbib,style=chicago-authordate,strict]{biblatex}
\input{biblatex-fix.tex}

% bibliography
\addbibresource{paper.bib}

\acrodef{CDER}{Canadian Center for Data Development and Economic Research}
\acrodef{PEI}{Prince Edward Island}
\acrodef{LEAP}{Longitudinal Employment Analysis Program}
\acrodef{BHP}{Establishment History Panel}
\acrodef{BR}{Business Register}
\acrodef{ILU}{Individual Labour Unit}
\acrodef{ALU}{Average Labour Unit}
\acrodef{LBD}{Longitudinal Business Database}
\acrodef{SynLBD}{Synthetic \ac{LBD}}
\acrodef{CBP}{County Business Patterns}
\acrodef{SBUSB}{Statistics of U.S. Businesses}
\acrodef{SEPH}{Survey of Employment, Payrolls and Hours}
\acrodef{LEHD}{Longitudinal Employer-Household Dynamics}
\acrodef{QWI}{{Q}uarterly {W}orkforce {I}ndicators}
\acrodef{BDS}{Business Dynamics Statistics}

\newcommand{\sym}[1]{\rlap{#1}}
\title{Applying Data Synthesis for Longitudinal Business Data across Three Countries }
\author{M. Jahangir Alam, Benoit Dostie, J\"org Drechsler, Lars Vilhuber\thanks{Corresponding author: Lars Vilhuber, \href{mailto:lars.vilhuber@cornell.edu}{lars.vilhuber@cornell.edu}. Alam was a part-time employee of Statistics Canada when this research was conducted. Drechsler is an employee of the Institut f\"ur Arbeitsmarktforschung, IAB. The opinions expressed here are those of the authors, and do not reflect the opinions of any of the statistical agencies involved. All results were reviewed for disclosure risks by their respective custodians, and released to the authors. Alam thanks Claudiu Motoc and Danny Leung for help with the Canadian data. Vilhuber acknowledges funding through NSF Grants SES-1131848 and SES-1042181, and a grant from Alfred P. Sloan Grant (G-2015-13903). Alam and Dostie acknowledge funding through SSHRC Partnership Grant ``Productivity, Firms and Incomes''. The creation of the Synthetic LBD  was funded by NSF Grant SES-0427889.}}
\begin{document}
\maketitle
\setstretch{1.5}
\begin{abstract}
\noindent
Data on businesses collected by statistical agencies are challenging to protect. Many businesses have unique characteristics, and distributions of employment, sales, and profits are highly skewed. Attackers wishing to conduct identification attacks often have access to much more information than for any individual. As a consequence, most disclosure avoidance mechanisms  fail to strike an acceptable balance between usefulness and confidentiality protection. Detailed aggregate statistics by geography or detailed industry classes  are rare, public-use microdata on business are virtually inexistant, and access to confidential microdata can be burdensome. 

Synthetic microdata have been proposed as a secure mechanism to publish microdata, as part of a broader discussion of how  to provide broader access to such datasets to researchers
In this article, we document an experiment to create analytically valid synthetic data, using the exact same model and methods previously employed for the United States, for data from two different countries: Canada (\ac{LEAP}) and Germany (\ac{BHP}). We assess utility, protection, and provide an assessment of the feasibility of extending such an approach in a cost-effective way to other data.

\end{abstract}


\newpage
\tableofcontents
\newpage
\acresetall
\section{Introduction}
\input{intro.tex}

\section{Data} 
\label{sec:data}
\input{data.tex}

%\section{Data Description: the German Case}
%\input{data.tex}

\todo{LARS STOPPED HERE}
\section{Methodology}
\label{sec:methodology}
\input{methodology.tex}

\section{Analytical validity}
\label{sec:analytic}
\input{analytic-validity.tex}

\section{Confidentiality protection}
\label{sec:confidentiality}
\input{confidentiality.tex}

\section{Conclusion and Extensions}
\label{sec:conclusion}
\input{conclusion.tex}



\newpage

\appendix{Supplementary Graphs}

\section{Analytical validity}

\subsection{Confidence interval for gross employment and other measures}
We compute the standard error for gross employment as follows. We consider gross employment $E$ to be the sum of firm employments $E_j$:

\begin{equation}
E = \sum_j E_j
\end{equation}

Average firm employment $\bar{E} = \frac{E}{N_j}$ is assumed to be normally distributed, with standard deviation $\sigma_{\bar{E}}$. We compare the synthetic and the confidential data for gross employment, including error bands.

\subsection{Confidence interval overlap measures}

More generally, the question as to the statistical precision of the results obtained from the synthetic data can be assessed. For this purpose, we computed the overlap of parameter estimates  as suggested by \cite{tas2006}. We compute the \emph{interval overlap measure} $J_{k,m}$ for parameter $k$ in model $m$. Consider the overlap of confidence intervals $(L,U)$ for $\beta_{k,m}$ (estimated from the confidential data) and $(L^{*},U^{*})$ for $\beta_{k,m}^*$ (from the synthetic data). Let $L^{over} = \max (L,L^{*} )$ and $U^{over} = \min (U,U^{*})$. Then the average overlap in confidence intervals is
$$
J_{k,m}^{*} = \frac{1}{2} \left [ \frac{U^{over} - L^{over}}{U-L} + \frac{U^{over} - L^{over}}{U^*-L ^*}        \right ]
$$
We then average $J_{k,m}^{*}$ over all estimated models and parameters, by validation request. The correct counterfactual involved running these validation requests against synthetic data that does not claim analytical validity, such as synthetic data generated from uni-dimensional distributions of variables. Results are pending.\todo{BD: ?}

%\subsection{Other models}
%
%Possible papers:
%
%\begin{itemize}
%%\item %\textcite{10.1257/aer.20141280} use the BDS to show the role of firm size in firm dynamics, but also had access to the Synthetic LBD.
%\item \textcite{NBERc0480} use a cross-country dataset to study average post-entry behavior of young firms. 
%\end{itemize}

%\bibliographystyle{apalike}
%\bibliography{paper}

\printbibliography

\end{document}